Order reduction and partial MILP models \\ for certifying Robustness of DNNs globally.

### 2025-07-26 AAAI2026/introduction.tex
intro (from ATVA)

\begin{table}[t!]
%	\vspace{-1.0cm}
	\centering
		\caption{Images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image. The 6 first DNNs are complex instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
	}
	\begin{tabular}{||l|c|c|c||c|c|c||}
		\hline
		Network & nbr & Accuracy {$^*$}  & Upper  {$^*$}& $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
		MNIST 5$\times$100 & 500 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
		$\epsilon = 0.026$ & ReLU & &  & 6.9s &  18.9s &  1026s  \\  \hline
		MNIST 5$\times$200 & 1000 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
		$\epsilon = 0.015$ & ReLU & &  & 6.5s &  16.6s &  930s  \\  \hline
		MNIST 8$\times$100 & 800 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
		$\epsilon = 0.026$ & ReLU &  &  & 7.2s &  20.1s &  930s  \\  \hline
		MNIST 8$\times$200 & 1600 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
		$\epsilon = 0.015$ & ReLU & &  & 6.8s &  18.2s &  1083s  \\  \hline
		MNIST 6$\times$500 & 3000 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
		CIFAR CNN-B--Adv &  16634  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
		CIFAR ResNet &   107496  & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
		$\epsilon = 8/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
	\end{tabular}
	\begin{minipage}{0.9\linewidth}
		\footnotesize
		{\textsuperscript{*} Accuracy means the accuracy of the network itself on test set, and Upper Bound is 100\% the percentage of unsafe examples.} \\
	\end{minipage}
	\label{table_beta}
%		\vspace{-0.5cm}
\end{table}

@@

\begin{table}[t!]
	\centering
%	\vspace{-0.35cm}
	\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
		%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
		Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
		}
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum &  Full MILP  \\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $49\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  4995s & 6100s
		  \\  \hline
		%  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $46\%$ & 37 \%    \\
		%  TO=2000s & &  & 1250s  & 1194s & 1466s \\  \hline	
	\end{tabular}
%	\vspace{-0.65cm}
\label{table_complete}
\end{table}

@@

\newpage

>>>>

\begin{table}[t!]
%	\vspace{-1.0cm}
	\centering
	\begin{tabular}{||l|c|c|c||c|c|c||}
		\hline
		Network & nbr & Accur.  & Upper & $\alpha,\beta$-CROWN& $\alpha,\beta$-CROWN & $\alpha,\beta$-CROWN \\ 
		Perturbation & activ. &  & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
		MNIST 5$\times$100 & 500 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
		$\epsilon = 0.026$ & ReLU & &  & 6.9s &  18.9s &  1026s  \\  \hline
		MNIST 5$\times$200 & 1000 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
		$\epsilon = 0.015$ & ReLU & &  & 6.5s &  16.6s &  930s  \\  \hline
		MNIST 8$\times$100 & 800 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
		$\epsilon = 0.026$ & ReLU &  &  & 7.2s &  20.1s &  930s  \\  \hline
		MNIST 8$\times$200 & 1600 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
		$\epsilon = 0.015$ & ReLU & &  & 6.8s &  18.2s &  1083s  \\  \hline
		MNIST 6$\times$500 & 3000 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
		$\epsilon = 0.035$ & ReLU & &  & 6.4s &  16.4s &  1003s  \\  \hline
		CIFAR CNN-B--Adv &  16634  &   78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
		$\epsilon = 2/255$& ReLU &  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
		CIFAR ResNet &   107496  & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
		$\epsilon = 8/255$ & ReLU &  &  & 2s & 2s & 2s  \\ \hline
	\end{tabular}
%	\begin{minipage}{0.9\linewidth}
%		\footnotesize
%		{\textsuperscript{*} Accuracy means the accuracy of the network itself on test set, and Upper Bound is 100\% the percentage of unsafe examples.} \\
%	\end{minipage}
		\caption{Accuracy of DNN (class predicted vs ground truth), upper bound on robustness (robustness attacks found on remaining images), and $\%$ of images verified by $\alpha,\beta$-CROWN with different time-outs (TO) on 7 DNNs, and average runtime per image. The 6 first DNNs are complex instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
	}
\label{table_beta}
%		\vspace{-0.5cm}
\end{table}

@@

\begin{table}[b!]
	\centering
%	\vspace{-0.35cm}
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum &  Full MILP  \\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $49\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  4995s & 6100s
		  \\  \hline
		%  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $46\%$ & 37 \%    \\
		%  TO=2000s & &  & 1250s  & 1194s & 1466s \\  \hline	
	\end{tabular}
%	\vspace{-0.65cm}
	\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
		%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
		Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-CROWN (40\%), at the cost of a much larger runtime (4995s vs 1026s).
		}
\label{table_complete}
\end{table}

@@

%\newpage
